\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-30 paper.tex
update title page
Filled out the title page with more information so it looks like other
MQPs and IQPs

% draw the title page
\maketitle

>>>>

% title page
\begin{center}
	{\huge ARuko and Editour: \\
		\Large A Platform for Augmented Reality Tour Guide Apps
	}

	\vfill

	A Major Qualifying Project \\
	Submitted to the faculty of \\
	WORCESTER POLYTECHNIC INSTITUTE \\
	In partial fulfillment of the requirements for the \\
	Degree of Bachelor of Science \par

	\vfill

	By \\
	William Campbell \\
	Cole Granof \\
	Joseph Petitti \par

	\vfill

	Date: \\
	October 11, 2019 \par

	\vfill

	Report submitted to: \par

	\vspace{\baselineskip}

\end{center}
\begin{flushright} % list your sponsors and advisers
	Atticus Sims, Sponsor \\
	Kyoto VR \par
	\vspace{\baselineskip}
	Professor Joshua Cuneo, Adviser \\
	Worcester Polytechnic Institute \par
	\vspace{\baselineskip}
	Professor Ralph Sutter, Adviser \\
	Worcester Polytechnic Institute \par
\end{flushright}

\vfill
